---
title: "p8105_hw1_mgg2153"
author: "mggn"
date: "9/16/2020"
output: github_document
---

## P8105 Homework 1
First, we need to load the tidyverse package to be able to call specific functions:

```{r load_tidy}
library(tidyverse)
```
Now, let's get started

### Problem 1 
Let's create a create a dataframe using the following code

```{r create_dataframe}
mg_dataf = 
  tibble(
    samp = rnorm(10),
    vec_logical = as.logical(samp > 0),
    vec_char = c("Hello", "world", "I", "am", "Maria", "and", "Frankie", "is","my", "pug"),
    factor_vec = factor(c("noun", "noun", "noun", "verb", "noun", "noun", "noun", "verb", "adj", "noun"))
  )
```

Then, I want to take the mean of each variable in my data frame. the purpose is to
see how R treats different variable types, and what happens when you try to take the
mean of these different variable types.

```{r var_means}
mean(pull(mg_dataf, samp))
mean(pull(mg_dataf, vec_logical))
mean(pull(mg_dataf, vec_char))
mean(pull(mg_dataf, factor_vec))
```

I can take the mean of my numeric and logical variables, but not of the character
or factor variables.Using the code below, we can try to convert the non-numeric
types into numeric variables:

```{r eval=FALSE}
as.numeric(pull(mg_dataf, vec_logical))
as.numeric(pull(mg_dataf, vec_char))
as.numeric(pull(mg_dataf, factor_vec))
```

And below, we can use the code to try and convert:  
  * logical type to numeric, and multiplying by a numeric variable  
  * logical to factor, and multiplying by a numeric variable  
  * logical to factor to numeric, and multiply by a numeric variable  
  
```{r convert_multiply}
as.numeric(pull(mg_dataf, vec_logical))*(pull(mg_dataf, samp))
as.factor(pull(mg_dataf, vec_logical))*(pull(mg_dataf, samp))
as.numeric(as.factor(pull(mg_dataf, vec_logical)))*(pull(mg_dataf, samp))
```

### Problem 2 - Penguins!

First, I want to load the penguins package per instruction on HW1. 

```{r load_penguins}
data("penguins", package = "palmerpenguins")

```
#### Overview: penguins dataset

The penguins dataset has **`r nrow(penguins)`** observations and **`r ncol(penguins)`** variables, 
which are: **`r names(penguins)`.** 

There are are three factor variables which are species, factor, and sex. 

For variable species, the categories are **`r levels(penguins$species)`**.
For variable island, the categories are **`r levels(penguins$island)`**.
For variable sex, the categories are **`r levels(penguins$sex)`**.

The other five variables are numeric types, which are summarized below:

flipper_length_mm:
the mean is **`r mean(na.omit(penguins$flipper_length_mm))`**.
the standard deviation is **`r sd(na.omit(penguins$flipper_length_mm))`**.

bill_length_mm:
the mean is **`r mean(na.omit(penguins$bill_length_mm))`**.
the standard deviation is **`r sd(na.omit(penguins$bill_length_mm))`**.

bill_depth_mm:
the mean is **`r mean(na.omit(penguins$bill_depth_mm))`**.
the standard deviation is **`r sd(na.omit(penguins$bill_depth_mm))`**.

body_mass_g:
the mean is **`r mean(na.omit(penguins$body_mass_g))`**.
the standard deviation is **`r sd(na.omit(penguins$body_mass_g))`**.

year:
the range of years in the dataset is from **`r min(penguins$year)`** to **`r max(penguins$year)`**.


### Scatterplot of bill length vs flipper length
We are looking at how these two variables behave:

```{r plotting}
ggplot(data = penguins, 
                       aes(x = bill_length_mm,
                           y = flipper_length_mm)) +
  geom_point(aes(color = species, 
                 shape = species)
  )

ggsave(file = 'first_penguins_scatter.png')
```




