---
title: "p8105_hw1_mgg2153"
author: "mggn"
date: "9/16/2020"
output: github_document
---

```{r}
library(tidyverse)
```

Problem 1: First, load the tidyverse library and create a dataframe using tibble

```{r}
mg_dataf = 
  tibble(
    samp = rnorm(10),
    vec_logical = as.logical(samp > 0),
    vec_char = c("Hello", "world", "I", "am", "Maria", "and", "Frankie", "is","my", "pug"),
    factor_vec = factor(c("noun", "noun", "noun", "verb", "noun", "noun", "noun", "verb", "adj", "noun"))
  )
print (mg_dataf)
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(mg_dataf, samp))
mean(pull(mg_dataf, vec_logical))
mean(pull(mg_dataf, vec_char))
mean(pull(mg_dataf, factor_vec))
```

penguins
```{r load_penguins}
data("penguins", package = "palmerpenguins")

names(penguins)
str(penguins)
levels(penguins$island)

```

The penguins dataset has 344 observations and 8 variables, which are: `r names(penguins)`. 
There are are three factor variables which are species, factor, and sex. 

For variable species, the categories are `r levels(penguins$species)`.
For variable island, the categories are `r levels(penguins$island)`.
For variable sex, the categories are `r levels(penguins$sex)`.


the size of the data set is
rlevels (penguins$island)
rlevels (penguins$species)
rncol(penguins)

`r round(mean(penguins$flipper_length_mm))`